# Data

## Technical description
In our project, we leverage data sourced from the Federal Bureau of Investigation's Crime Data Explorer (accessible at https://cde.ucr.cjis.gov/LATEST/webapp/#/pages/downloads), curated by Xinran She. Our focus is on analyzing the causes of arrests categorized by crime, with an emphasis on distinguishing between adult and juvenile arrests. To this end, we utilize three datasets: "Reported Number of Adult Arrests by Crime," "Reported Number of Juvenile Arrests by Crime," and "Hate Crime 2022". These records are reliable because only data from agencies that provided arrest records for 12 months of the year can be included. Meanwhile, they are in CSV format, which can be directly imported and read in R, offering ease of access and compatibility for our subsequent data visualization efforts.

### Reported Number of Adult Arrests by Crime
This dataset comprises data on the monthly count of adult arrests for a range of offenses, as reported by cooperating law enforcement agencies, spanning 1995 to 2016. The file was last modified in 2017 and is now completed. The dataset includes 644 rows and 47 columns. Each row of the data represents an offense reason based on a specific year, and the columns decompose the count of the arrested adults by age, race, and sex. The age range of offenders covered by this form is 18-65 years old. From the website, agencies might not provide race information, but age and sex should be clearly reported. So, some of the missing gender information may affect the subsequent visualization and analysis.

### Reported Number of Juvenile Arrests by Crime
Similar to 2.1-1, this dataset records the monthly count of juvenile arrests for different offenses, as reported by participating law enforcement agencies from 1995 to 2016. The file was last modified in 2017 and is now completed. The dataset includes 690 rows and 27 columns. Each row of the data represents an offense reason based on a specific year, and the columns decompose the count of the arrested adults by age, race, and sex. The age range of offenders covered by this form is 9-17 years old. The potential problem with the data is the same as 2.1-1 due to the insufficiency of race information.

### Hate Crime 2022
The hate crime dataset compiles annual data from 1991 to 2022, last updated in 2023, encompassing details on incidents, offenses, and involved individuals - both victims and offenders - in crimes driven by the perpetrator's bias towards the victim's race, gender, gender identity, religion, disability, sexual orientation, or ethnicity. Due to the extensive size of the original file, our analysis is concentrated on the data from 2022. This dataset segment contains 11,643 rows and 28 columns, each representing an individual incident and providing comprehensive incident details, including geographical location, numbers of victims and offenders, and the nature of the bias involved. A challenge presented by this dataset is its considerable size and the abundance of categorical data it contains. To effectively glean insights, engaging in data manipulation, compiling, and analyzing aggregate information is necessary.

## Research plan
Based on the previous questions we proposed in **introduction** part, we've structured our investigation into three key stages: imputing missing values, manipulating and aggregating data, and conducting visualization and analysis.

Regarding our first research question, we plan to explore the relationship between identity factors like age, gender, or race, and crime arrests among juveniles and adults. To effectively depict these associations, we'll employ various graphical representations. These will include basic bar charts for straightforward comparisons, stacked bars to illustrate the combined effects of multiple factors, and scatter plots to examine correlations or similarities between the two demographic groups. Meanwhile, we plan to use mosaic plots to visually represent data encompassing two or more qualitative variables, which is particularly effective for illustrating the relationships.
For the second question, which seeks to identify the most prevalent motivations behind crimes, our approach will involve the use of simple bar charts. These charts will display the relative frequency of different offense types, offering a clear view of the most common factors leading to criminal activity.

For the third research question, focusing on the trends in arrest populations and the relationship within socio-economic factors. Line graphs will be our primary tool to depict the trends in arrest numbers over various years, with years plotted on the x-axis and arrest counts on the y-axis. To analyze the interplay between multiple socio-economic factors alongside these trends, we will use multi-line charts. These charts will simultaneously display how each socio-economic variable changes over the same period, allowing for a comprehensive comparison and correlation analysis.

Similarly for the fourth question, focusing on the highest hate crime state and with some specific bias type, we will utilize pie charts to effectively illustrate the proportion of each bias type. Additionally, for a more granular analysis of categories like location types, offender races, and bias types, treemaps will be employed as they offer a concise visual summary. For instance, in a treemap, each major section could represent a distinct bias type, further divided into sub-sections based on offender race or location type. This approach provides an intuitive and detailed view of the hate crime data, highlighting key patterns and distributions.

## Missing value analysis

### First load our dataset:
```{r}
arrest_juvenile = read.csv("preprocessing/arrests_national_juvenile.csv")
arrest_adults = read.csv("preprocessing/arrests_national_adults.csv")
hate_crime22 = read.csv("preprocessing/hate_crime_2022.csv")
```
### Use aggregated missing patterns to check missing values in each dataset:
**Arrest_juvenile**
```{r}
#| fig-width: 50
#| fig-height: 20
#| out-width: 80%
library(redav)
library(ggplot2)
plot_missing(arrest_juvenile, percent = FALSE)+
  theme_bw(5)
```

The column "state_abbr" (state abbreviation)is completely absent. Unfortunately, we couldn't find other datasets which perfectly make up for the lack of state abbreviation. Since our main goal is not about discovering arrest crimes in specific states, we decide to drop "state_abbr" column. We have several missing values in "american_indian" and "asian_pacific_islander", which are more likely to be missing due to "not all agencies report race and/or ethnicity for arrests" from the FBI. We also have missing values in "f_0_9", f_0_12", "m_0_9", "f_13_14", "f_15", "m_10_12", "f_16" in decreasing order. Even though "all agencies must report age and sex", it is hard to implement in reality. By intuition, these omissions might stem from the actual absence of instances, given that the corresponding class values are zero. For example, in 2016, there is a missing value for males aged between 0 to 9 arrested for Embezzlement. Given the unlikely occurrence of embezzlement by children under 10, it is reasonable to impute it as 0. Since missing values are not correlated with other variables and take up only a small percent, we would impute 0 for the missing values in those columns.

**Arrest_adults**
```{r}
#| fig-width: 70
#| fig-height: 20
#| out-width: 80%
plot_missing(arrest_adults, percent = FALSE)+
  theme_bw(5)
```

Similarly, the column "state_abbr" (state abbreviation)is entirely missing. This time, we have fewer columns with missing values, only "f_60_64", f_65_p", "f_55_59" in decreasing order. In other words, we can see missing values are concentrated in females aged between 55 to 65+. The interesting pattern might caused by certain oversight when reporting elderly women in the agencies. Or, it may be attributed to the likelihood that women aged above 55 are hardly prone to crimes, which is reasonable for us to interpret the corresponding class values as 0. Since missing values are not correlated with other variables and take up only a small percent, we would impute 0 for the missing values in those columns.

**Hate Crime**
```{r}
#| fig-width: 60
#| fig-height: 20
#| out-width: 80%
plot_missing(hate_crime22, percent = FALSE)+
  theme_bw(5)
```

We have equal number of missing values in "adult_offender_count" and "juvenile_offender_count". They are correlated because in each hate crime incident, agencies either report all the offenders, or they fail to report. The number of missing value of "juvenile_victim_count" is slightly higher than "adult_victim_count". One of the possible explanation is that the agencies are more likely to protect the privacy of juvenile that they choose not to report in the reality. We also have missing values in "total_individual_victims", given "total_individual_victims" is likely correlated with "juvenile_victim_count" and  "adult_victim_count". Since for **Hate Crime**, we are more interested in the "location, offender race and bias type" instead of the number of offenders and victims, we could subset the dataset to drop the columns with missing values.
